### 2019-01-26 soc.tex
update annotation translation
create references at the end of the paper
add packages for including images and for captions
add list of figures to the end of the paper
add \newpage before each \section

@@

@@

% title formatting
\titleformat{\section}{\bfseries\scshape\fontsize{18}{21.6}\selectfont}{\thesection}{1em}{}
\titleformat{\subsection}{\bfseries\fontsize{16}{19.2}\selectfont}{\thesubsection}{1em}{}
\titleformat{\subsubsection}{\bfseries\fontsize{14}{16.8}\selectfont}{\thesubsubsection}{1em}{}

@@

  \section*{\normalfont\textbf{Anotace}}
  Tato práce popisuje proces tvorby webové stránky \url{robotics-simplified.com}. Stránka zpracovává témata z oboru robotiky formou pochopitelnou i naprostým začátečníkem. Je poháněna generátorem statických stránek Jekyll, který doplňují JavaSriptové knihovny pro vykreslování matematických rovnic, analýzy návštěvnosti a interaktivní vizualizaci probíraných konceptů. Komprese obrázků, nahrání obsahu na hosting přes FTP, převod stránky do její knižní podoby pro offline čtení a mnoho dalšího jsou plně automatizovány pomocí scriptů psaných v jazyce Python.

  \section*{\normalfont\textbf{Klíčová slova}}
  robotika; webová stránka; vzdělávání

  \section*{\normalfont\textbf{Annotation}}
  This paper decribes the process of creating the \url{robotics-simplified.com} website. The site explores topics in the field of robotics in a beginner-friendly way. It is powered by the static site generator Jekyll, and is suplemented by JavaScript libraries used for rendering mathematical equations, analyzing the website traffic and visualizing the discussed concepts. Image compression, content upload via FTP and conversion of the website to a book version are fully automated using Python scripts.

  \section*{\normalfont\textbf{Keywords}}
  robotics; website; education

@@

>>>>

% image and caption include setup
\usepackage{graphicx}
\graphicspath{ {./img/} }

@@

% figure caption setup
\usepackage[font=small,labelfont=bf]{caption}
\renewcommand{\figurename}{Obr. č.}

@@

% title formatting
\titleformat{\section}{\newpage\bfseries\scshape\fontsize{18}{21.6}\selectfont}{\thesection}{1em}{}
\titleformat{\subsection}{\bfseries\fontsize{16}{19.2}\selectfont}{\thesubsection}{1em}{}
\titleformat{\subsubsection}{\bfseries\fontsize{14}{16.8}\selectfont}{\thesubsubsection}{1em}{}

@@

  \subsection*{\fontsize{18}{21.6}\selectfont\normalfont\textbf{Anotace}}
  Tato práce popisuje proces tvorby webové stránky \url{robotics-simplified.com}. Stránka zpracovává témata z oboru robotiky formou pochopitelnou i naprostým začátečníkem. Je poháněna generátorem statických stránek Jekyll, který doplňují JavaSriptové knihovny pro vykreslování matematických rovnic, analýzy návštěvnosti a interaktivní vizualizaci probíraných konceptů. Komprese obrázků, nahrání obsahu na hosting přes FTP, převod stránky do její knižní podoby pro offline čtení a mnoho dalšího jsou plně automatizovány pomocí scriptů psaných v jazyce Python.

  \subsection*{\fontsize{18}{21.6}\selectfont\normalfont\textbf{Klíčová slova}}
  robotika; webová stránka; vzdělávání

  \subsection*{\fontsize{18}{21.6}\selectfont\normalfont\textbf{Annotation}}
  This paper decribes the process of creating the \url{robotics-simplified.com} website. The site covers topics in the field of robotics in a beginner-friendly way. It is powered by the static site generator Jekyll, and is suplemented by JavaScript libraries used for rendering mathematical equations, analyzing the website traffic and visualizing the discussed concepts. Image compression, content upload via FTP and conversion of the website to a book version are fully automated using Python scripts.

  \subsection*{\fontsize{18}{21.6}\selectfont\normalfont\textbf{Keywords}}
  robotics; website; education

@@

  % create the bibliography with the proper formating and a czech name and add it to TOC
  \renewcommand{\refname}{Použitá literatura}
  \addcontentsline{toc}{section}{Použitá literatura}
  \bibliographystyle{czechiso}
  \bibliography{soc}

  % create the list of figures and add it to TOC
  \renewcommand{\listfigurename}{Seznam obrázků a tabulek}
  \addcontentsline{toc}{section}{Seznam obrázků a tabulek}
  {%
  \let\oldnumberline\numberline%
  \renewcommand{\numberline}{\figurename~\oldnumberline}%
  \listoffigures%
  }
